### 2016-11-08 text/ms.Rmd
Tweak links

\noindent where $\hat{B}_{t+1}$ represents predicted biomass at time $t$ plus
one year, $B_t$ represents biomass at time $t$, $r$ represents intrinsic
population growth rate, $B_0$ represents unfished biomass or carrying capacity
$K$, and $C$ represents catch. The fourth model is an empirically derived model
based on the RAM Legacy Stock Assessment Database [@ricard2012]. @rosenberg2014
provide a full background on these four methods \R{C} 
(<http://www.fao.org/docrep/019/i3491e/i3491e00.htm>, last accessed 2016-09-27) 
and code to fit all the models
is available in an accompanying package `datalimited` for the statistical
software R [@r2015] <https://github.com/datalimited/datalimited> 
(last accessed 2016-09-27). In summary:

@@

Fishing scenarios included three levels of initial biomass depletion
compared to carrying capacity: biomass at 100%, 70%, and 40% of carrying
capacity; and four exploitation patterns: (1) a constant exploitation rate,
(2) an exploitation rate coupled with biomass to mimic an open-access
single-species fishery, (3) a scenario where exploitation rate increased
continuously, and (4) a "roller-coaster" scenario where the exploitation
rate increased and then decreased. Process noise (recruitment variability;
i.e., unexplained variability in population dynamics) was introduced to the
models at two magnitudes in log space, $N(0, 0.2^2)$ and $N(0, 0.6^2)$,
and was either uncorrelated through time or had first-order autoregressive
correlation of $0.6$. The simulation also included a scenario with $N(0,
0.2^2)$ measurement error around log catch  and one scenario without
measurement error. @rosenberg2014 ran ten iterations for each combination
of factors adding stochastic draws of recruitment and catch-recording
variability each time to generate a total of 5760 stocks. 
Code to generate the simulations is available at
<https://github.com/iagomosqueira/stockStatusFAO> (last accessed 2016-09-27).

@@

Predictive performance can be evaluated with metrics that represent a variety
of modelling goals. For continuous response variables such as the mean and
slope of population status, performance metrics often measure some form of
bias, precision, accuracy (a combination of bias and precision), or the ability
to correctly rank or correlate across populations [e.g., @walther2005]. Here, we
measure proportional error, defined as $(\hat{\theta} - \theta)/\abs{\theta}$,
where $\hat{\theta}$ and $\theta$ represent estimated and "true" (or
stock-assessed) mean or slope of $B/B_\mathrm{MSY}$. We calculated median
proportional error to measure bias, median absolute proportional error to
measure accuracy, and Spearman's rank-order correlation between predicted and
"true" values to measure the ability to correctly rank populations. When
testing with the RAM Legacy Stock Assessment database, we treated the
estimates from these data-rich stock assessments as known without error. Thus,
any error in the stock-assessment estimates of the mean or slope of
$B/B_\mathrm{MSY}$ also contributes to our estimates of prediction error for
each of the four data-limited models and the ensembles. Code to reproduce our
analysis is available at <https://github.com/datalimited/ensembles> (last accessed 2016-09-27).

>>>>

\noindent where $\hat{B}_{t+1}$ represents predicted biomass at time $t$ plus
one year, $B_t$ represents biomass at time $t$, $r$ represents intrinsic
population growth rate, $B_0$ represents unfished biomass or carrying capacity
$K$, and $C$ represents catch. The fourth model is an empirically derived model
based on the RAM Legacy Stock Assessment Database [@ricard2012]. @rosenberg2014
provide a full background on these four methods \R{C} 
(<http://www.fao.org/docrep/019/i3491e/i3491e00.htm>, last accessed 2016-11-08) 
and code to fit all the models
is available in an accompanying package `datalimited` for the statistical
software R [@r2015] <https://github.com/datalimited/datalimited> 
(last accessed 2016-11-08). In summary:

@@

Fishing scenarios included three levels of initial biomass depletion
compared to carrying capacity: biomass at 100%, 70%, and 40% of carrying
capacity; and four exploitation patterns: (1) a constant exploitation rate,
(2) an exploitation rate coupled with biomass to mimic an open-access
single-species fishery, (3) a scenario where exploitation rate increased
continuously, and (4) a "roller-coaster" scenario where the exploitation
rate increased and then decreased. Process noise (recruitment variability;
i.e., unexplained variability in population dynamics) was introduced to the
models at two magnitudes in log space, $N(0, 0.2^2)$ and $N(0, 0.6^2)$,
and was either uncorrelated through time or had first-order autoregressive
correlation of $0.6$. The simulation also included a scenario with $N(0,
0.2^2)$ measurement error around log catch  and one scenario without
measurement error. @rosenberg2014 ran ten iterations for each combination
of factors adding stochastic draws of recruitment and catch-recording
variability each time to generate a total of 5760 stocks. 
Code to generate the simulations is available at
<https://github.com/datalimited/stocksims> (last accessed 2016-11-08).

@@

Predictive performance can be evaluated with metrics that represent a variety
of modelling goals. For continuous response variables such as the mean and
slope of population status, performance metrics often measure some form of
bias, precision, accuracy (a combination of bias and precision), or the ability
to correctly rank or correlate across populations [e.g., @walther2005]. Here, we
measure proportional error, defined as $(\hat{\theta} - \theta)/\abs{\theta}$,
where $\hat{\theta}$ and $\theta$ represent estimated and "true" (or
stock-assessed) mean or slope of $B/B_\mathrm{MSY}$. We calculated median
proportional error to measure bias, median absolute proportional error to
measure accuracy, and Spearman's rank-order correlation between predicted and
"true" values to measure the ability to correctly rank populations. When
testing with the RAM Legacy Stock Assessment database, we treated the
estimates from these data-rich stock assessments as known without error. Thus,
any error in the stock-assessment estimates of the mean or slope of
$B/B_\mathrm{MSY}$ also contributes to our estimates of prediction error for
each of the four data-limited models and the ensembles. Code to reproduce our
analysis is available at <https://github.com/datalimited/ensembles> (last accessed 2016-11-08).
